Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-10-20 paper/paper.qmd
Updating authors

---
title: "Race to the Ballot Box: Will Demographics Decide a Winner This Year?"
subtitle: "A Regressional Approach to Race and Political Preferences in the 2024 US Elections and Insights on the Next"
author: 
  - Sameeck Bhatia
  - Sean Chua
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Proin semper lobortis ante quis euismod. Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi. Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id. Praesent mi nisi, venenatis nec euismod a, vehicula et nisl. In hac habitasse platea dictumst. Sed tristique ligula id suscipit convallis. Donec eget orci in felis consequat fringilla id sit amet lacus."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Race to the Ballot Box: Will Demographics Decide a Winner This Year?"
subtitle: "A Regressional Approach to Race and Political Preferences in the 2024 US Elections and Insights on the Next"
author: 
  - Sameeck Bhatia
  - Sean Chua
  - Tanmay Shinde
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Proin semper lobortis ante quis euismod. Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi. Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id. Praesent mi nisi, venenatis nec euismod a, vehicula et nisl. In hac habitasse platea dictumst. Sed tristique ligula id suscipit convallis. Donec eget orci in felis consequat fringilla id sit amet lacus."
format: pdf
number-sections: true
bibliography: references.bib
---
